Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-18 pkg/disttree/inst/draft/draft.Rnw
final revision and formatting
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2470 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: bc69d6b1df1a94a14c4954e27896487bb7cffb6f

A distributional model $\mathcal{D}(Y, \bm{\theta})$ is considered for the response
variable $Y \in \mathcal{Y}$ using the distributional family $\mathcal{D}$ with
\textit{k}-dimensional parameter vector $\bm{\theta} \in \bold{\Theta}$ and
corresponding log-likelihood function $\ell(\bm{\theta}; Y)$. The GAMLSS
framework \citep{Rigby+Stasinopoulos:2005} provides a wide range of such
distributional families with parameterizations corresponding to location, scale,
and shape. Furthermore, censoring and/or truncation of these distributions
can be incorporated in the usual straightforward way
\citep[see e.g.,][Chapter~7.2]{Long:1997}.

@@

With the specification of the distribution family and its log-likelihood 
function the task of fitting a distributional model turns into the task 
of estimating the distribution parameter~$\bm{\theta}$. This is commonly done by
maximum likelihood (ML) based on the learning sample with observations
$\{y_i\}_{i = 1, \dots, n}$ of the response variable $Y$. The maximum
likelihood estimator (MLE) $\bm{\hat \theta}$ is given by
\begin{equation}
\label{eq:mle}
\bm{\hat \theta} = \argmax_{\bm{\theta} \in \bold{\Theta}} \sum_{i=1}^n \ell(\bm{\theta}; y_i).
\end{equation}
Equivalently, this can be defined based on the corresponding first-order
conditions
\begin{equation}
\label{eq:foc}
\sum_{i = 1}^n s(\bm{\hat{\theta}}, y_i) = 0,
\end{equation}
where $s(\bm{\theta}; y_i)$ is the associated score function
\begin{equation}
\label{eq:score}
s(\bm{\theta}; y_i) = \frac{\partial \ell}{\partial \bm{\theta}}(\bm{\theta}; y_i).
\end{equation}
The latter is subsequently employed as a general goodness-of-fit measure
to assess how well the distribution with parameters $\bm{\theta}$ fits
one individual observation $y_i$.

@@

Typically, a single global model $\mathcal{D}(Y, \bm{\theta})$ is not sufficient
for reasonably representing the response distribution. Therefore, covariates
$\bold{Z} = Z_1, \dots, Z_m \in \mathcal{Z}$ are
employed to capture differences in the distribution parameters $\bm{\theta}$.
In weather forecasting, these covariates typically include the output
from numerical weather prediction systems and/or lagged meteorological observations.

To incorporate the covariates into the distributional model, 
they are considered as regressors in additive predictors
$g_j(\theta_j) = f_{j,1}(\bold{Z}) + f_{j,2}(\bold{Z}) + \dots$
in GAMLSS.
Link functions $g_j(\cdot)$ are used for every parameter $\theta_j$
($j = 1, \dots, k$) based on smooth terms $f_{j,k}$ such as
nonlinear effects, spatial effects, random coefficients, or interaction surfaces
\citep{Klein+Kneib+Lang:2015}. However, this requires specifying the
additive terms and their functional forms in advance which can be challenging in
practice and potentially require expert knowledge in the application domain, 
especially if the number of covariates $m$ is large.

@@

For obtaining probabilistic predictions from the tree for a (possibly new) set
of covariates $\bold{z} = (z_1, \ldots, z_m)$, the observation simply has to
be ``sent down'' the tree and the corresponding segment-specific MLE has to be
obtained. Thus, in practice $\bm{\hat \theta}(\bold{z})$ does not have to be 
recalculated for each new $\bold{z}$ but one can simply extract the parameter estimates 
for the corresponding segment which have been computed already while
learning the tree. However, to understand this estimator conceptually it is useful
to denote it as a weighted MLE where the weights select those observations from 
the learning sample that fall into the same segment:
\begin{equation}
w^{\text{tree}}_i(\bold{z}) = \sum_{b=1}^B \mathbf{1}((\bold{z}_i \in \mathcal{B}_b) \land (\bold{z} \in \mathcal{B}_b)),
\end{equation}
where $\mathbf{1}(\cdot)$ is the indicator function. The predicted distribution
for a given $\bold{z}$ is then fully specified by the estimated parameter
$\bm{\hat \theta}(\bold{z})$ where
\begin{equation}
\bm{\hat \theta}(\bold{z}) = \argmax_{\bm{\theta} \in \bm{\Theta}} \sum_{i=1}^n w^{\text{tree}}_i(\bold{z}) \cdot \ell(\bm{\theta}; y_i).
\end{equation}

@@

The idea of random forests is to learn an ensemble of trees, each on a different
learning data obtained through resampling (bootstrap or subsampling). In each node 
only a random subset of the covariates $\bold{Z}$ is considered for splitting to reduce the 
correlation among the trees and to stabilize the variance of the model.
For a simple regression random forest the mean of predictions over
all trees is considered. In that way changes in the location  of the response 
across the covariates are detected (e.g., in Breiman and Cutler's random forests, 
\citealp{Breiman:2001}).
This idea is now taken one step further by embedding it in a distributional 
framework based on maximum-likelihood estimation. \emph{Distributional forests} 
employ an ensemble of $T$~\emph{distributional trees} which pick up changes in 
the ``direction'' of any distribution parameter by considering the full likelihood
and corresponding score function for choosing splitting variables and split points.

To obtain probabilistic predictions from a distributional forest, it still
needs to be specified how to compute the parameter estimates
$\bm{\hat \theta}(\bold{z})$ for a (potentially new) set of covariates $\bold{z}$.
Following \cite{Hothorn+Zeileis:2017} we interpret random forests as adaptive
local likelihood estimators using the averaged ``nearest neighbor weights''
\citep{Lin+Jeon:2006} from the $T$~trees in the forest
\begin{equation}
w^{\text{forest}}_i(\bold{z}) = \frac{1}{T} \sum_{t=1}^T \sum_{b=1}^{B^t}
\frac{\mathbf{1}((\bold{z}_i \in \mathcal{B}^t_b) \land (\bold{z} \in \mathcal{B}^t_b))}{|\mathcal{B}^t_b|},
\end{equation}
where $|\mathcal{B}^t_b|$ denotes the number of observations in the $b$-th
segment of the $t$-th tree.
Thus, these $w^{\text{forest}}_i(\bold{z}) \in [0, 1]$ whereas
$w^{\text{tree}}_i(\bold{z}) \in \{0, 1\}$. Hence, weights cannot only be $0$
or $1$ but change more smoothly, giving high weight to those observations $i$
from the learning sample that co-occur in the same segment $\mathcal{B}_b^t$
as the new observation $\bold{z}$ for many of the trees $t = 1, \dots, T$.
Consequently, the parameter estimates may, in principle, change for every
observation and can be obtained by
\begin{equation}
\bm{\hat \theta}(\bold{z}) =  \argmax_{\bm{\theta} \in \bm{\Theta}} \sum_{i=1}^n w^{\text{forest}}_i(\bold{z}) \cdot \ell(\bm{\theta}; y_i).
\end{equation}
In summary, this yields a parametric distributional regression model 
(through the score-based approach) that can capture both abrupt effects and
high-order interactions (through the trees) and smooth effects (through
the forest).

@@

In a first step, we show a detailed comparison of the competing models
for one observation site, Axams in Tyrol (in the center of the study area,
see Figure~\ref{fig:all-map}). As for all other stations, daily precipitation 
observations and numerical weather predictions are available for the month of July 
from 1985 through 2012. In Figure~\ref{fig:axams-dist} in the introduction the 
probabilistic forecasts from the distributional forest, trained on 1985--2008, 
for July 24 in 2009--2012 have already been shown as a motivational example. 
\hlc{In particular, the figure depicts the forecasted point mass at zero
(i.e., the probability of a dry day) along with the forecasted probability 
density function for the total amount of precipitation. Based on this illustration 
it can be observed that} the four sample forecasts differ considerably in 
location $\mu$, scale $\sigma$, and the amount of censoring while conforming quite 
well with the actual observations from these days. 
While this is a nice illustrative example we are  
interested in the overall predictive performance and calibration of the
distributional fits. More details of this assessment as well as
an application to 14~further meteorological stations is provided in
Supplement~B \citep{Schlosser+Hothorn+Stauffer:2018b}.

To assess calibration, Figure~\ref{fig:axams-qq} shows residual QQ~plots for
out-of-sample predictions (2009--2012) from the different models trained on
1985--2008. Due to the point masses at zero 100 draws from the randomized
quantile residuals \citep{Dunn+Smyth:1996} are plotted in semi-transparent
gray. Overall, the randomized quantile residuals conform quite well with the
theoretical standard normal quantile (i.e., form a straight line close to the 
diagonal), indicating that all four models are sufficiently well calibrated. 
This is also supported by the corresponding probability integral transform
(PIT, \citealp{Gneiting+Balabdaoui+Raftery:2007}) histograms for station
Axams in Supplement~B \citep{Schlosser+Hothorn+Stauffer:2018b} which 
contains a more detailed explanation of residual QQ plots and PIT histograms.

@@

To assess whether these differences in predictive performance are due to differences
in the topography, Figure~\ref{fig:all-map} shows a brief spatial summary of all
stations. Each station is illustrated by a symbol that conveys which
model performed best in terms of CRPS on the last 4~years of the data.
Additionally, the color of the symbol indicates the CRPS difference between 
distributional forest and the best-performing other model. Green signals that
the distributional forest performs better than the other models whereas red
signals that another model performs better. Overall the distributional forest
performs on par (gray) or better (green) for the majority of stations. Only
for a few stations in the north-east EMOS performs best, and in East Tyrol
the prespecified GAMLSS performs particularly well in the validation period
(2009--2012). \hlc{Partially, this can be attributed to random variation as
the differences at several stations are mitigated when considering a full
cross-validation rather than a single split into learning and validation period}
\citep[see Supplement~A,][and the corresponding discussion in the next section]{Schlosser+Hothorn+Stauffer:2018a}.
\hlc{Further differences are possibly due to East Tyrol lying in a different
climate zone, south of the main Alpine Ridge. Hence, long-term climatological
characteristics as well as the precipitation patterns in 2009--2012 differ
from North Tyrol, conforming particularly well with the additive effects from
the prespecified GAMLSS.}

@@

Choosing an adequate distributional family is an important step for
establishing a well-fitting model. A zero-censored Gaussian distribution is
employed in this manuscript as this has been found to be an appropriate choice
for precipitation modeling in earlier literature
\citep[e.g.,][]{Stauffer+Mayr+Messner:2017}. 
To test for robustness against distributional misspecifation, 
two alternative distributional specifications have been considered
in Supplement~A \citep{Schlosser+Hothorn+Stauffer:2018a}: Using the
same evaluations as in Section~\ref{sec:all}, all models are
additionally fitted for 15~meteorological stations using a zero-censored
logistic distribution in order to account for heavier tails and a two-part
Gaussian hurdle model combining a binary model for zero vs.~positive
precipitation and a separate Gaussian model, truncated at zero, for the
positive precipitation observations. Both specifications yield qualitatively 
similar results as for the zero-censored Gaussian distribution. For some stations
the two-part hurdle model leads to small improvements, however at the expense
of increased variability across stations (especially for EMOS and the 
boosted GAMLSS). Overall, the results from this manuscript are quite
robust across these distributional specifications, especially for the
distributional forests.

@@

Axams was chosen as the meteorological station for the more extensive evaluations
in Section~\ref{sec:axams} as it yields fairly typical results
and is geographically in the center of the study area and closest to
Innsbruck, the capital of Tyrol and the work place of three of the authors.
To show that qualitatively similar results are obtained for other
meteorological stations, Supplement~B \citep{Schlosser+Hothorn+Stauffer:2018b}
carries out the same evaluation for 14~further stations. These
cover a wide range of geographical locations/altitudes and a mix of
different best-performing models in the single-split setting reported in
Section~\ref{sec:all}.

@@

\section*{Computational details}
\label{sec:comp}

@@

The fitted distributional forest for July 24 and
observation station Axams (including Figure~\ref{fig:axams-dist})
is reproducible using \code{demo("RainAxams", package = "disttree")}.
This also includes fitting the other zero-censored
Gaussian models considered in this paper and generating the corresponding 
QQ~plots (Figure~\ref{fig:axams-qq}) and PIT histograms 
\citep[Supplement~B]{Schlosser+Hothorn+Stauffer:2018b}.
Full replication of all results can be obtained with
\code{demo("RainTyrol", package = "disttree")}
requiring the companion \textsf{R} package \textbf{RainTyrol} 
(version~\Sexpr{packageVersion("RainTyrol")}),
also available within the \textsf{R}-Forge~project.
The results presented in Supplement~A \citep{Schlosser+Hothorn+Stauffer:2018a} and 
Supplement~B \citep{Schlosser+Hothorn+Stauffer:2018b} can be reproduced using
\code{demo("RainDistributions", package = "disttree")} and 
\code{demo("RainStationwise", package = "disttree")}, respectively.

>>>>

A distributional model $\mathcal{D}(Y, \bm{\theta})$ is considered for the response
variable $Y \in \mathcal{Y}$ using the distributional family $\mathcal{D}$ with
\textit{k}-dimensional parameter vector $\bm{\theta} \in \bm{\Theta}$ and
corresponding log-likelihood function $\ell(\bm{\theta}; Y)$. The GAMLSS
framework \citep{Rigby+Stasinopoulos:2005} provides a wide range of such
distributional families with parameterizations corresponding to location, scale,
and shape. Furthermore, censoring and/or truncation of these distributions
can be incorporated in the usual straightforward way
\citep[see e.g.,][Chapter~7.2]{Long:1997}.

@@

With the specification of the distribution family and its log-likelihood 
function the task of fitting a distributional model turns into the task 
of estimating the distribution parameter~$\bm{\theta}$. This is commonly done by
maximum likelihood (ML) based on the learning sample with observations
$\{y_i\}_{i = 1, \dots, n}$ of the response variable $Y$. The maximum
likelihood estimator (MLE) $\bm{\hat \theta}$ is given by
\begin{equation}
\label{eq:mle}
\bm{\hat \theta} = \argmax_{\bm{\theta} \in \bm{\Theta}} \sum_{i=1}^n \ell(\bm{\theta}; y_i).
\end{equation}
Equivalently, this can be defined based on the corresponding first-order
conditions
\begin{equation}
\label{eq:foc}
\sum_{i = 1}^n s(\bm{\hat{\theta}}, y_i) = 0,
\end{equation}
where $s(\bm{\theta}; y_i)$ is the associated score function
\begin{equation}
\label{eq:score}
s(\bm{\theta}; y_i) = \frac{\partial \ell}{\partial \bm{\theta}}(\bm{\theta}; y_i).
\end{equation}
The latter is subsequently employed as a general goodness-of-fit measure
to assess how well the distribution with parameters $\bm{\theta}$ fits
one individual observation $y_i$.

@@

Typically, a single global model $\mathcal{D}(Y, \bm{\theta})$ is not sufficient
for reasonably representing the response distribution. Therefore, covariates
$\bm{Z} = Z_1, \dots, Z_m \in \mathcal{Z}$ are
employed to capture differences in the distribution parameters $\bm{\theta}$.
In weather forecasting, these covariates typically include the output
from numerical weather prediction systems and/or lagged meteorological observations.

To incorporate the covariates into the distributional model, 
they are considered as regressors in additive predictors
$g_j(\theta_j) = f_{j,1}(\bm{Z}) + f_{j,2}(\bm{Z}) + \dots$
in GAMLSS.
Link functions $g_j(\cdot)$ are used for every parameter $\theta_j$
($j = 1, \dots, k$) based on smooth terms $f_{j,k}$ such as
nonlinear effects, spatial effects, random coefficients, or interaction surfaces
\citep{Klein+Kneib+Lang:2015}. However, this requires specifying the
additive terms and their functional forms in advance which can be challenging in
practice and potentially require expert knowledge in the application domain, 
especially if the number of covariates $m$ is large.

@@

For obtaining probabilistic predictions from the tree for a (possibly new) set
of covariates $\bm{z} = (z_1, \ldots, z_m)$, the observation simply has to
be ``sent down'' the tree and the corresponding segment-specific MLE has to be
obtained. Thus, in practice $\bm{\hat \theta}(\bm{z})$ does not have to be 
recalculated for each new $\bm{z}$ but one can simply extract the parameter estimates 
for the corresponding segment which have been computed already while
learning the tree. However, to understand this estimator conceptually it is useful
to denote it as a weighted MLE where the weights select those observations from 
the learning sample that fall into the same segment:
\begin{equation}
w^{\text{tree}}_i(\bm{z}) = \sum_{b=1}^B \mathbf{1}((\bm{z}_i \in \mathcal{B}_b) \land (\bm{z} \in \mathcal{B}_b)),
\end{equation}
where $\mathbf{1}(\cdot)$ is the indicator function. The predicted distribution
for a given $\bm{z}$ is then fully specified by the estimated parameter
$\bm{\hat \theta}(\bm{z})$ where
\begin{equation}
\bm{\hat \theta}(\bm{z}) = \argmax_{\bm{\theta} \in \bm{\Theta}} \sum_{i=1}^n w^{\text{tree}}_i(\bm{z}) \cdot \ell(\bm{\theta}; y_i).
\end{equation}

@@

The idea of random forests is to learn an ensemble of trees, each on a different
learning data obtained through resampling (bootstrap or subsampling). In each node 
only a random subset of the covariates $\bm{Z}$ is considered for splitting to reduce the 
correlation among the trees and to stabilize the variance of the model.
For a simple regression random forest the mean of predictions over
all trees is considered. In that way changes in the location  of the response 
across the covariates are detected (e.g., in Breiman and Cutler's random forests, 
\citealp{Breiman:2001}).
This idea is now taken one step further by embedding it in a distributional 
framework based on maximum-likelihood estimation. \emph{Distributional forests} 
employ an ensemble of $T$~\emph{distributional trees} which pick up changes in 
the ``direction'' of any distribution parameter by considering the full likelihood
and corresponding score function for choosing splitting variables and split points.

To obtain probabilistic predictions from a distributional forest, it still
needs to be specified how to compute the parameter estimates
$\bm{\hat \theta}(\bm{z})$ for a (potentially new) set of covariates $\bm{z}$.
Following \cite{Hothorn+Zeileis:2017} we interpret random forests as adaptive
local likelihood estimators using the averaged ``nearest neighbor weights''
\citep{Lin+Jeon:2006} from the $T$~trees in the forest
\begin{equation}
w^{\text{forest}}_i(\bm{z}) = \frac{1}{T} \sum_{t=1}^T \sum_{b=1}^{B^t}
\frac{\mathbf{1}((\bm{z}_i \in \mathcal{B}^t_b) \land (\bm{z} \in \mathcal{B}^t_b))}{|\mathcal{B}^t_b|},
\end{equation}
where $|\mathcal{B}^t_b|$ denotes the number of observations in the $b$-th
segment of the $t$-th tree.
Thus, these $w^{\text{forest}}_i(\bm{z}) \in [0, 1]$ whereas
$w^{\text{tree}}_i(\bm{z}) \in \{0, 1\}$. Hence, weights cannot only be $0$
or $1$ but change more smoothly, giving high weight to those observations $i$
from the learning sample that co-occur in the same segment $\mathcal{B}_b^t$
as the new observation $\bm{z}$ for many of the trees $t = 1, \dots, T$.
Consequently, the parameter estimates may, in principle, change for every
observation and can be obtained by
\begin{equation}
\bm{\hat \theta}(\bm{z}) =  \argmax_{\bm{\theta} \in \bm{\Theta}} \sum_{i=1}^n w^{\text{forest}}_i(\bm{z}) \cdot \ell(\bm{\theta}; y_i).
\end{equation}
In summary, this yields a parametric distributional regression model 
(through the score-based approach) that can capture both abrupt effects and
high-order interactions (through the trees) and smooth effects (through
the forest).

@@

In a first step, we show a detailed comparison of the competing models
for one observation site, Axams in Tyrol (in the center of the study area,
see Figure~\ref{fig:all-map}). As for all other stations, daily precipitation 
observations and numerical weather predictions are available for the month of July 
from 1985 through 2012. In Figure~\ref{fig:axams-dist} in the introduction the 
probabilistic forecasts from the distributional forest, trained on 1985--2008, 
for July 24 in 2009--2012 have already been shown as a motivational example. 
\hlc{In particular, the figure depicts the forecasted point mass at zero
(i.e., the probability of a dry day) along with the forecasted probability 
density function for the total amount of precipitation. Based on this illustration 
it can be observed that} the four sample forecasts differ considerably in 
location $\mu$, scale $\sigma$, and the amount of censoring while conforming quite 
well with the actual observations from these days. 
While this is a nice illustrative example we are  
interested in the overall predictive performance and calibration of the
distributional fits. More details of this assessment as well as
an application to 14~further meteorological stations is provided in
Supplement~B \citep{Schlosser+Hothorn+Stauffer:2019b}.

To assess calibration, Figure~\ref{fig:axams-qq} shows residual QQ~plots for
out-of-sample predictions (2009--2012) from the different models trained on
1985--2008. Due to the point masses at zero 100 draws from the randomized
quantile residuals \citep{Dunn+Smyth:1996} are plotted in semi-transparent
gray. Overall, the randomized quantile residuals conform quite well with the
theoretical standard normal quantile (i.e., form a straight line close to the 
diagonal), indicating that all four models are sufficiently well calibrated. 
This is also supported by the corresponding probability integral transform
(PIT, \citealp{Gneiting+Balabdaoui+Raftery:2007}) histograms for station
Axams in Supplement~B \citep{Schlosser+Hothorn+Stauffer:2019b} which 
contains a more detailed explanation of residual QQ plots and PIT histograms.

@@

To assess whether these differences in predictive performance are due to differences
in the topography, Figure~\ref{fig:all-map} shows a brief spatial summary of all
stations. Each station is illustrated by a symbol that conveys which
model performed best in terms of CRPS on the last 4~years of the data.
Additionally, the color of the symbol indicates the CRPS difference between 
distributional forest and the best-performing other model. Green signals that
the distributional forest performs better than the other models whereas red
signals that another model performs better. Overall the distributional forest
performs on par (gray) or better (green) for the majority of stations. Only
for a few stations in the north-east EMOS performs best, and in East Tyrol
the prespecified GAMLSS performs particularly well in the validation period
(2009--2012). \hlc{Partially, this can be attributed to random variation as
the differences at several stations are mitigated when considering a full
cross-validation rather than a single split into learning and validation period}
\citep[see Supplement~A,][and the corresponding discussion in the next section]{Schlosser+Hothorn+Stauffer:2019a}.
\hlc{Further differences are possibly due to East Tyrol lying in a different
climate zone, south of the main Alpine Ridge. Hence, long-term climatological
characteristics as well as the precipitation patterns in 2009--2012 differ
from North Tyrol, conforming particularly well with the additive effects from
the prespecified GAMLSS.}

@@

Choosing an adequate distributional family is an important step for
establishing a well-fitting model. A zero-censored Gaussian distribution is
employed in this manuscript as this has been found to be an appropriate choice
for precipitation modeling in earlier literature
\citep[e.g.,][]{Stauffer+Mayr+Messner:2017}. 
To test for robustness against distributional misspecifation, 
two alternative distributional specifications have been considered
in Supplement~A \citep{Schlosser+Hothorn+Stauffer:2019a}: Using the
same evaluations as in Section~\ref{sec:all}, all models are
additionally fitted for 15~meteorological stations using a zero-censored
logistic distribution in order to account for heavier tails and a two-part
Gaussian hurdle model combining a binary model for zero vs.~positive
precipitation and a separate Gaussian model, truncated at zero, for the
positive precipitation observations. Both specifications yield qualitatively 
similar results as for the zero-censored Gaussian distribution. For some stations
the two-part hurdle model leads to small improvements, however at the expense
of increased variability across stations (especially for EMOS and the 
boosted GAMLSS). Overall, the results from this manuscript are quite
robust across these distributional specifications, especially for the
distributional forests.

@@

Axams was chosen as the meteorological station for the more extensive evaluations
in Section~\ref{sec:axams} as it yields fairly typical results
and is geographically in the center of the study area and closest to
Innsbruck, the capital of Tyrol and the work place of three of the authors.
To show that qualitatively similar results are obtained for other
meteorological stations, Supplement~B \citep{Schlosser+Hothorn+Stauffer:2019b}
carries out the same evaluation for 14~further stations. These
cover a wide range of geographical locations/altitudes and a mix of
different best-performing models in the single-split setting reported in
Section~\ref{sec:all}.

@@

\section*{Computational details}

@@

The fitted distributional forest for July 24 and
observation station Axams (including Figure~\ref{fig:axams-dist})
is reproducible using \code{demo("RainAxams", package = "disttree")}.
This also includes fitting the other zero-censored
Gaussian models considered in this paper and generating the corresponding 
QQ~plots (Figure~\ref{fig:axams-qq}) and PIT histograms 
\citep[Supplement~B]{Schlosser+Hothorn+Stauffer:2019b}.
Full replication of all results can be obtained with
\code{demo("RainTyrol", package = "disttree")}
requiring the companion \textsf{R} package \textbf{RainTyrol} 
(version~\Sexpr{packageVersion("RainTyrol")}),
also available within the \textsf{R}-Forge~project.
The results presented in Supplement~A \citep{Schlosser+Hothorn+Stauffer:2019a} and 
Supplement~B \citep{Schlosser+Hothorn+Stauffer:2019b} can be reproduced using
\code{demo("RainDistributions", package = "disttree")} and 
\code{demo("RainStationwise", package = "disttree")}, respectively.
